Rapid technological progress in white light-emitting diodes \\ and its sources in innovation and technology spillovers

### 2023-08-10 2_SSL_NE/article/article_main.tex

\hypersetup{
    pdftitle={Hybrid Life-Cycle Methods},
    pdfauthor={Michael Weinold, Sergey Kolesnikov, Laura Diaz Anadon},
}

@@

M. Weinold$^{1,2,3}$, S. Kolesnikov$^3$, L.D. Anadon$^{3,4}$ \\
\newline
$^1$ CEENRG, Dept. of Land Economy, University of Cambridge, Cambridge,  UK \\
$^2$ ETH Zurich, Zurich, Switzerland \\
$^3$ Technology Assessment Group, Paul Scherrer Institute, Villigen, Switzerland \\
$^4$ Belfer Center for Science and International Affairs, Harvard University, Cambridge MA, USA

>>>>

\hypersetup{
    pdftitle={Main Article},
    pdfauthor={Michael Weinold, Sergey Kolesnikov, Laura Diaz Anadon},
}

@@

M. Weinold$^{1,2,3}$, S. Kolesnikov$^3$, L.D. Anadon$^{3,4}$ \\
\newline
$^1$ CEENRG, Dept. of Land Economy, University of Cambridge, Cambridge,  UK \\
$^2$ Group for Energy Systems Analysis, Department of Mechanical and Process Engineering, ETH Zurich, Zurich, Switzerland \\
$^3$ Technology Assessment Group, Paul Scherrer Institute, Villigen, Switzerland \\
$^4$ Belfer Center for Science and International Affairs, Harvard University, Cambridge MA, USA

### 2023-08-10 2_SSL_NE/article/article_supplementary.tex

@@

% custom figure and table numbering
\renewcommand{\thefigure}{SI\arabic{figure}}
\renewcommand{\thetable}{SI\arabic{table}}

@@

\hypersetup{
    pdftitle={Hybrid Life-Cycle Methods},
    pdfauthor={Michael Weinold, Sergey Kolesnikov, Laura Diaz Anadon},
}

@@

\setlength{\fboxsep}{10pt}
\fbox{
    \parbox{\textwidth}{
        \textit{\textsc{Supplementary Information}} for: \\
        \newline 
        M. Weinold$^{1,2,3}$, S. Kolesnikov$^3$, L.D. Anadon$^{3,4}$ \\
        "Rapid technological progress in white light-emitting diodes and its sources in innovation and technology spillovers" \textit{Nature Energy} (2023) \\
        \newline
        $^1$ Technology Assessment Group, Paul Scherrer Institute, Switzerland \\
        $^2$ ETH Zurich, Zurich, Switzerland \\
        $^3$ CEENRG, Dept. of Land Economy, University of Cambridge, UK \\
        $^4$ Belfer Center for Science and International Affairs, Harvard University, Cambridge MA, USA
    }
}

>>>>

% nature energy custom code

\newcounter{supplementarynote}
\renewcommand{\thesupplementarynote}{\arabic{supplementarynote}}
\newcommand{\supplementarynote}{%
  \refstepcounter{supplementarynote}%
  Supplementary Note~\thesupplementarynote:~%
}
\titleformat{\section}
  {\normalfont\large\bfseries}
  {\supplementarynote}
  {0em} % Adjust this value to control the spacing
  {}
\renewcommand{\thesection}{\thesupplementarynote}

@@

% custom figure and table numbering
\renewcommand{\thefigure}{Supplementary Figure \arabic{figure}}
\renewcommand{\thetable}{SI\arabic{table}}

@@

\hypersetup{
    pdftitle={Supplement},
    pdfauthor={Michael Weinold, Sergey Kolesnikov, Laura Diaz Anadon},
}

@@

\setlength{\fboxsep}{10pt}
\fbox{
    \parbox{\textwidth}{
        \textit{\textsc{Supplementary Information}} for: \\
        \newline 
        M. Weinold$^{1,2,3}$, S. Kolesnikov$^3$, L.D. Anadon$^{3,4}$ \\
        "Rapid technological progress in white light-emitting diodes and its sources in innovation and technology spillovers" (2023) \\
        \newline
        $^1$ Technology Assessment Group, Paul Scherrer Institute, Switzerland \\
        $^2$ Group for Energy Systems Analysis, Department of Mechanical and Process Engineering, ETH Zurich, Zurich, Switzerland \\
        $^3$ CEENRG, Dept. of Land Economy, University of Cambridge, UK \\
        $^4$ Belfer Center for Science and International Affairs, Harvard University, Cambridge MA, USA
    }
}
